Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Updated the incorrect endings to the three re-implementations

%Relate it to categories
Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identifed.

@@

%%Relate it to Categories
%%What she said
The addition of axserialport was requested by API users. A possible use case, which was given during the interiew involved a ticketing system which allows for joint analysis of data from both devices. As such it was included in version 2.0, to meet the demand of the API users.

@@

@@

@@

The interviewee again described how the main intent to changing this part of the API came about most to bring it into line with the new event driven and callback focused architecture. Similarly to the previous change, this feature was redesigned and re-implemented with added functionality.

Our conclusion of enhancive and groomative was also backwards for this change. As per the previous change, the primary intent was to bring these parts of the API into line with the new standard; improving functionality was an added bonus.

@@

The interviewee once again clarified how this change was indeed primarily concerned with meeting the new standards of version 2.0. They agreed that little had actually changed in terms of what functionality the API offered and gave the same reasoning suggested for the two prior changes.

Once again our conclusion was incorrect for the categorisation of this change. Given the information from the interview, we deemed that this change was also primarily groomative with a subcategory of enhancive.

>>>>

%Relate it to categories
Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified.

@@

%%Relate it to Categories
%%What she said
The addition of axserialport was requested by API users. A possible use case, which was given during the interview involved a ticketing system which allows for joint analysis of data from both devices. As such it was included in version 2.0, to meet the demand of the API users.

@@

The interviewee outline that the previous version of axevent, event, was deprecated in favour of a redesigned event system. This redesign was also a good opportunity to implement the new interface design.

@@

From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.

@@

The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.

Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.

@@

The interviewee clarified that this change was mainly concerned with implementing new functionality and re-implementing old functionality while simultaneously adopting the new standards of version 2.0.

Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
